Article template&#58; A reproducible RMarkdown template for Elsevier's journal format with examples for beginners

### 2019-02-12 Paper/Manuscript.Rmd
Re-order sections, add plots

``` {r libraries, echo=FALSE, cache=FALSE, results="hide", message=FALSE, warning = FALSE}
## code chunk for libraries that are required to be installed + loaded for this template
# note the first word after `{r...` in the chunk header above is the name of this chunk. 
# Names must be unique and not have spaces (underscores are ok), so name with CamelCaseLikeThis or snake_case_like_this
require(tidyverse)
#require(ggExtra)
#require(gridExtra)
require(here)
require(knitr)
require(stargazer)
#require(RColorBrewer)
#require(ggrepel)
#require(ggpmisc)
require(gt)
```

@@

@@

```{r}
df %>% 
    sample_n(5) %>%   # select 5 random rows from the dataframe
    select(iris_class, sepal_length, petal_length, petal_length_level) %>%  # show only these columns (in this order)
    gt () %>% #make a table
    tab_header( 
    title = "Example irises", # ...with this title
    subtitle = "Data on five randomly selected irises")

@@

## Other packages
Here are lots of packages that are useful for markdown docs. I encourage you to search for these whenever you encounter a new thing you need to do and to propose an addition to this repository accordingly. For example, the Stargazer package describes linear models in a nice table.

``` {r linmods, results='asis', echo=FALSE, warning=FALSE}
lm1 = lm(hwy ~ displ + cyl + year, mpg)
lm2 = lm(cty ~ displ + cyl + year, mpg)
# uncomment next line for printing in console (i.e. human readable in RStudio)
#stargazer(lm1, lm2, type="text")
stargazer(lm1, lm2, dep.var.labels=c("Highway","City"), covariate.labels=c("Displacement","Num. cylinders", "Year"), title = "Car miles per gallon", column.sep.width = "1pt", header=FALSE)
```

@@

# Writing style
This is a little off topic for an Rmd example but a convenient place to remind our grad students about writing style. In almost all cases, active voice is better than passive voice. Several psychological studies show that the active voice is more easily understood by readers, and that information is more accurately reported by authors when writing in active voice. For example, research @klenbortMarkednessPerspectiveInterpretation1974 has shown that the “active [voice] offers a neutral structure for conveying information”. Authorship guides for highly regarded journals often indicate a preference for the active voice instead of passive:

@@

## A fun way to spot passive voice:
If you can add the words ‘by zombies’ @ScaryeasyWayHelp2014 to the end of the sentence and the sentence still makes logical sense, then the sentence is in passive voice. You can also switch on the grammar settings in Microsoft Word’s spelling and grammar checker and it will show up that way.

@@

# Results

@@

>>>>

``` {r libraries, echo=FALSE, cache=FALSE, results="hide", message=FALSE, warning = FALSE}
## code chunk for libraries that are required to be installed + loaded for this template
# note the first word after `{r...` in the chunk header above is the name of this chunk. 
# Names must be unique and not have spaces (underscores are ok), so name with CamelCaseLikeThis or snake_case_like_this
require(tidyverse)
#require(ggExtra)
#require(gridExtra)
require(here)
require(knitr)
require(stargazer)
#require(RColorBrewer)
#require(ggrepel)
require(ggpmisc)
require(gt)
```

@@

 You may wish to have short sub-sections for:

 - Terminology
 - Objectives

@@

```{r irisTable}
df %>% 
    sample_n(5) %>%   # select 5 random rows from the dataframe
    select(iris_class, sepal_length, petal_length, petal_length_level) %>%  # show only these columns (in this order)
    gt () %>% #make a table
    tab_header( 
    title = "Example irises", # ...with this title
    subtitle = "Data on five randomly selected irises")

@@

The instructions for installing BetterBibtex are [here](https://retorque.re/zotero-better-bibtex/).

### Add note on citing software
- TODO

## Other packages
There are lots of packages that are useful for markdown docs. We encourage you to search for these whenever you encounter a new thing you need to do and to propose an addition to this repository accordingly.`

@@

Here is another equation:

$$ CD_{rated} = \frac{4*Q}{\pi*D^2} = 2.0~m/s$$

## Writing style
This is a little off topic for an Rmd example but a convenient place to remind our grad students about writing style. In almost all cases, active voice is better than passive voice. Several psychological studies show that the active voice is more easily understood by readers, and that information is more accurately reported by authors when writing in active voice. For example, research @klenbortMarkednessPerspectiveInterpretation1974 has shown that the “active [voice] offers a neutral structure for conveying information”. Authorship guides for highly regarded journals often indicate a preference for the active voice instead of passive:

@@

### A fun way to spot passive voice:
If you can add the words ‘by zombies’ @ScaryeasyWayHelp2014 to the end of the sentence and the sentence still makes logical sense, then the sentence is in passive voice. You can also switch on the grammar settings in Microsoft Word’s spelling and grammar checker and it will show up that way.

@@

# Results
Figure \@ref(fig:irises) shows petal widths by iris type.

```{r irises, message=FALSE, fig.width =8, fig.height = 4.5, fig.cap = "Petal and sepal lengths from iris dataset" }
ggplot(df, aes(x = petal_length, y = sepal_length, group = iris_class)) + 
  geom_smooth(method=lm, se=FALSE, size = 0.5, linetype = "solid", color = "darkgray") +
  geom_point(aes(color = iris_class, shape = long_sepal), alpha = 0.6, size=3) +
  coord_cartesian(xlim = c(0,9), ylim = c(0,9)) + 
  stat_poly_eq(formula = y~x, 
               aes(color=iris_class, label = paste(..eq.label.., sep = "~~~")), 
               parse = TRUE, label.y = c(2, 2.5, 3), 
               label.x = 7, hjust = 1, size = 3.5) +
  scale_y_continuous(expand=c(0,0),expression(Petal~length ~ (cm))) +
  scale_x_continuous(expand=c(0,0),expression(Sepal~length (cm))) +
  guides(color=guide_legend(title="Class",
                            reverse=T, override.aes = list(shape = 15, size=3)), 
         shape=guide_legend(title="long_sepal")) +
  scale_color_manual (values = cal_palette4)
```

## Violin plot
Figure \@ref(fig:petalwidths) shows petal widths by iris type.

``` {r petalwidths, message=FALSE, fig.width = 6, fig.height = 4, fig.cap = "Petal widths by class" }
df %>%
    ggplot() + 
    geom_violin(aes( x = iris_class, y = petal_width, color = iris_class), draw_quantiles = T, trim = F, show.legend = F) +
    geom_boxplot(aes( x = iris_class, y = petal_width, color = iris_class), width = 0.07, show.legend = F)+
    ggtitle("Petal widths by species") +
    scale_color_manual(values=cal_palette4)

@@

# Limitations
It is important to include a discussion of limitations in any paper. Limitations of this template include:

- Figures are included after the text, not at the location where they are discussed in the text
